The eclipse of ASASSN-21qj

### 2022-08-22 src/tex/ms.tex
added EEM multi

>>>>

ERIC NEW:
ASASSN-21qj (Gaia DR3 5539970601632026752 = 2MASS J08152329-3859234) has a neighbor (Gaia DR3 5539970597334497024= 2MASS J08152298-3859244) a few arcseconds away for which we checked to see if it could plausibly be a physical companion.
%
Based on the Gaia EDR3 mean ICRS position for epoch 2016.0, the visual companion lies
at separation $\rho$ = $3738.243\pm0.062$ mas at position angle $\theta$ = $249^{\circ}.977$.
%
Their parallaxes ($\varpi$ = $1.7631\pm0.0112$ mas vs. $1.4711\pm0.0523$ mas)
differ by 5.5$\sigma$ and proper motions ($\mu_{\alpha} = -9.692\pm0.012$, $\mu_{\delta} = 7.349\pm0.012$ \masyr\, vs. $\mu_{\alpha} = -0.114\pm0.055$, $\mu_{\delta} = 6.419\pm0.053$ \masyr) differ by a factor of 2.
%
If the two stars are at the parallactic distance of ASASSN-21qj
\citep[$d$ = 552.4 pc;][]{BailerJones21}, then their difference in proper motion ($\Delta\mu$ = $9.623\pm0.056$ \masyr) translates to a difference in tangential velocity of $\Delta V_{tan}$ = $25.37\pm0.21$ \kms.
%
The velocity difference is considerable given the projected separation of 2079\,au.
%
Using Kepler's 3rd law, and assuming the observed separation corresponded
to the semi-major axis, and the observed $\Delta V_{tan}$ corresponded to the
full orbital velocity, these quantities would predict a minimum system mass of
$>$1509 \Msun.
%
Based on the implausible estimated dynamical mass inferred from the observed separation and difference in tangential velocities, we conclude that the
visual companion Gaia DR3 5539970597334497024 (2MASS J08152298-3859244) is an interloper
unrelated to ASASSN-21qj.

:
